The Impact of Uncertainty on Monetary Transmission

### 2023-10-17 US/draft.Rmd
Dealt with seasonal adjustment issues

```{=latex}
\begin{figure}[!htbp]
```
```{r}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R') %>% 
  filter(spec == 'shadow',
         control == 'financial_stress',
         index == 'epu',
         thresh == '0.7') %>% 
  ggplot(aes(x = t, y = median)) +
  geom_line(linewidth = lw) +
  geom_hline(yintercept = 0, color = "red") +
  facet_wrap(regime~label, scales = "free")+
  theme_minimal() +
  theme(plot.title = element_text(size = 11, hjust=0.5),
        axis.title.y = element_text(size=11),
        legend.position = 'none') +
  labs(x = "",
       y ="")
```
```{=latex}
\caption{Regime specific impulse responses, updated specification. \label{fig:epumedirfs}}
\bigskip
\footnotesize
\textit{Notes}: Interest rates are measured by the Shadow Rate, the threshold value is set to the 70th percentile of the EPU index.
\end{figure}
```

@@

```{=latex}
\begin{figure}[!htbp]
```
```{r narrative, fig.height=10}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R',
         spec == 'shadow',
         index != 'epu',
         control == 'financial_stress') %>% 
  group_by(label, regime, spec, control, thresh, index) %>% 
  mutate(median = purrr::accumulate(.x = median, 
                                    .f = sum,
                                    .dir = 'forward'),
         upper = purrr::accumulate(.x = upper, 
                                    .f = sum,
                                    .dir = 'forward'),
         lower = purrr::accumulate(.x = lower, 
                                    .f = sum,
                                    .dir = 'forward')) %>% 
  filter(t == max(t)) %>% 
  select(-t, -upper, -lower) %>% 
  spread(label, median) %>% 
  mutate(sac = Y/PI,
         regime = str_remove_all(regime, ' uncertainty'),
         thresh = case_when(thresh == '0.5' ~ 'Median',
                            thresh == '0.7' ~ '70th Perc.'),
         thresh = factor(thresh, levels = c('Median', '70th Perc.')),
         index = case_when(index == 'epu' ~ 'EPU',
                           index == 'epu_debt' ~ 'EPU: Debt, crises',
                           index == 'epu_finreg' ~ 'EPU: Fin. Regulation',
                           index == 'epu_fis' ~ 'EPU: Fiscal Policy',
                           index == 'epu_mon' ~ 'EPU: Monetary Policy',
                           index == 'epu_reg' ~ 'EPU: Regulation',
                           index == 'epu_trade' ~ 'EPU: Trade Policy')) %>% 
  ggplot(aes(x = regime, y = sac, fill = regime)) + 
  geom_col( color = 'black', width = 0.3, position = position_dodge(width = 0.1)) +
  facet_grid(index~thresh, scales = 'free') +
  theme_minimal()+
  theme(legend.position = 'none') +
  labs(x = '',
       y = '') + 
  scale_fill_manual(breaks = c('High',
                                'Low'),
                     values = c('#8B0000',
                                '#00008B'))

>>>>

```{=latex}
\begin{figure}[!htbp]
```
```{r}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R') %>% 
  filter(spec == 'shadow',
         control == 'both',
         index == 'epu',
         thresh == '0.7') %>% 
  ggplot(aes(x = t, y = median, ymin = lower, ymax = upper)) +
  geom_line(linewidth = lw) +
  geom_hline(yintercept = 0, color = "red") +
  geom_ribbon(alpha = .2)+
  facet_wrap(regime~label, scales = "free")+
  theme_minimal() +
  theme(plot.title = element_text(size = 11, hjust=0.5),
        axis.title.y = element_text(size=11),
        legend.position = 'none') +
  labs(x = "",
       y ="")
```
```{=latex}
\caption{Regime specific impulse responses, updated specification. \label{fig:epumedirfs}}
\bigskip
\footnotesize
\textit{Notes}: Interest rates are measured by the Shadow Rate, the threshold value is set to the 70th percentile of the EPU index.
\end{figure}
```

@@

```{=latex}
\begin{figure}[!htbp]
```
```{r narrative, fig.height=10}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R',
         spec == 'shadow',
         index != 'epu',
         control == 'both') %>% 
  group_by(label, regime, spec, control, thresh, index) %>% 
  mutate(median = purrr::accumulate(.x = median, 
                                    .f = sum,
                                    .dir = 'forward'),
         upper = purrr::accumulate(.x = upper, 
                                    .f = sum,
                                    .dir = 'forward'),
         lower = purrr::accumulate(.x = lower, 
                                    .f = sum,
                                    .dir = 'forward')) %>% 
  filter(t == max(t)) %>% 
  select(-t, -upper, -lower) %>% 
  spread(label, median) %>% 
  mutate(sac = Y/PI,
         regime = str_remove_all(regime, ' uncertainty'),
         thresh = case_when(thresh == '0.5' ~ 'Median',
                            thresh == '0.7' ~ '70th Perc.'),
         thresh = factor(thresh, levels = c('Median', '70th Perc.')),
         index = case_when(index == 'epu' ~ 'EPU',
                           index == 'epu_debt' ~ 'EPU: Debt, crises',
                           index == 'epu_finreg' ~ 'EPU: Fin. Regulation',
                           index == 'epu_fis' ~ 'EPU: Fiscal Policy',
                           index == 'epu_mon' ~ 'EPU: Monetary Policy',
                           index == 'epu_reg' ~ 'EPU: Regulation',
                           index == 'epu_trade' ~ 'EPU: Trade Policy')) %>% 
  ggplot(aes(x = regime, y = sac, fill = regime)) + 
  geom_col( color = 'black', width = 0.3, position = position_dodge(width = 0.1)) +
  facet_grid(index~thresh, scales = 'free') +
  theme_minimal()+
  theme(legend.position = 'none') +
  labs(x = '',
       y = '') + 
  scale_fill_manual(breaks = c('High',
                                'Low'),
                     values = c('#8B0000',
                                '#00008B'))
